Figures for conference paper

### 2019-04-25 conference figures.Rmd
rescale 2 figures (2 beta distrib)

```{r plot_beta}
plot_beta <- function(topic = 1, sub = NULL){

@@

@@

  ggsave(filename = str_c("Beta - topic ", topic, ".jpeg"), path = output_folder,
         width = plot_width, height = plot_height)

@@

```{r fig_gamma}
plot_gamma("HUM1014", sub = "HUM1014 is characterized by topics 43 (philosophy) and 26 (literature)", course_title = "HUM1014 Great Novels 1850 - Present")

plot_beta(43, sub = "Topic 43 corresponds to the theme of philosophy")

plot_beta(26, sub = "Topic 26 corresponds to the theme of literature")
```

@@

      subgraph cluster_inter_first{
      label = '';
      style = filled;
		  color = white;
      TE [label = 'Topic Expertise']
      AP [label = 'Academic Performance']
      }

@@

      # Intermediate nodes
      node [color = black]
      TM [label = 'Topic Model']
      PM [label = 'Predictive Models']
      TR [label = 'Student´s Transcript']

@@

      edge[label = '']
      {AP, TE} -> x2 [arrowhead = none]
      edge[label = ' Lasso', decorate = TRUE]
      x2 -> PM;

      edge[label = '']
      {TM, AI} -> x1 [arrowhead = none]
      edge[label = 'KL distance', decorate = TRUE]
      x1 -> SUG;

>>>>

```{r plot_beta}
plot_beta <- function(topic = 1, sub = NULL, resize_factor = 1){

@@

    theme(axis.text.y = element_text(size = 11)) +

@@

  ggsave(filename = str_c("Beta - topic ", topic, ".jpeg"), path = output_folder,
         width = plot_width / resize_factor, height = plot_height / resize_factor)

@@

```{r fig_gamma}
plot_gamma("HUM1014", sub = "HUM1014 is dominated by topics 43 (philosophy) and 26 (literature)", course_title = "HUM1014 Great Novels 1850 - Present")

resize_factor <- 1.6

plot_beta(43, sub = "Theme of philosophy", resize_factor = resize_factor)

plot_beta(26, sub = "Theme of literature", resize_factor = resize_factor)
```

@@

      subgraph cluster_inter_first{
      label = '';
      style = filled;
		  color = white;
      AP [label = 'Academic Performance']
      TR [label = 'Student´s Transcript']
      TE [label = 'Topic Expertise']
      }

@@

      # Intermediate nodes
      node [color = black]
      TM [label = 'Topic Model']
      PM [label = 'Predictive Models']

@@

      edge[label = '']
      {AP, TE} -> x1 [arrowhead = none]
      edge[label = ' Lasso', decorate = TRUE]
      x1 -> PM;

      edge[label = '']
      {TM, AI} -> x2 [arrowhead = none]
      edge[label = 'KL distance', decorate = TRUE]
      x2 -> SUG;
